---
title: "Project Proposal"
author: "Cho YongSoo"
date: "`r Sys.Date()`"
output: rmarkdown::html_document

---



```{r setup, include = FALSE}
#You do not need to touch this chunk
#words after "#" sign are treated as comments
#It is strongly recommanded to use English in r markdown
knitr::opts_chunk$set(echo = TRUE)
```


# Rmarkdown template(Title)

## 1.Write comments(Section)
You can write sentences here like MS Word or Hangul. You can also write greek letters like $\alpha$, $\beta$, and $\gamma$ and mathematical symbols like $\Sigma$, $\forall$ and $\propto$ etc. You can find this by googling.

### 1.1 Calculation(Subsection)
You can calculate something between paragraph using chunks.
```{r cal}
round(pi^2/6)
```

### 1.2 Easy plot
You can plot something like below:
```{r plot1}
x=rnorm(100)
y=x+rnorm(100,sd=0.5)
plot(x,y,main="My Simulated Data")
```

### 1.3 Complex Plot
```{r plot2, echo=FALSE}
#echo=FALSE to hide codes
#results='hide' to hide results
mu<-10.75
sig<- .8

par(mar=c(3,3,1,1),mgp=c(1.75,.75,0))
par(mfrow=c(1,2))

x<- seq(7.9,13.9,length=500)
plot(x,pnorm(x,mu,sig),type="l",ylab=expression(paste(italic("F"),"(",italic("y"),")")),xlab=
    expression(italic(y)),lwd=1)
abline(h=c(0,.5,1),col="gray")
plot(x,dnorm(x,mu,sig),type="l",ylab=expression(paste(italic("p"),"(",italic("y"),")")),
xlab=
  expression(italic(y)),lwd=1)
abline(v=mu,col="gray")
```

### 1.3 table
You can draw table
```{r table, results='asis'}
#results='asis' option for xtable package
library(datasets)
data(airquality)
fit=lm(Ozone~Wind+Temp+Solar.R,data=airquality)
library(xtable)
#Need to install xtable package before
xt=xtable(summary(fit))
print(xt,type="html")
```

